Attempting to predict Heart Disease using a classical decision tree machine learning method

### 2022-12-08 Manuscript/paper.tex
fixed data visualization images

  \includegraphics[width=\textwidth]{heartdisease_and_gender.png}

@@

  \label{fig:heartdisease_and_gender}

@@

Figure~\ref{fig:heartdisease_and_gender} shows that within this data set more females did not have heart disease than females who did. The opposite is evidently true for males, more males had heart disease in the data set than males who did not have heart disease. 

@@

  \includegraphics[width=\textwidth]{age_heartdisease.png}

@@

  \includegraphics[width=\textwidth]{cholesterol_heartdisease.png}

@@

%CHANGE THE IMAGE PUT IN THE WRONG ONE

@@

  \includegraphics[width=\textwidth]{RestingBloodPressure_Heartdisease.png}

@@

%\bibliography{refs}
%\bibliographystyle{ama}

>>>>

  \includegraphics[width=\textwidth]{Sex_HeartDisease.png}

@@

  \label{fig:heartdisease_and_sex}

@@

Figure~\ref{fig:heartdisease_and_sex} shows that within this data set more females did not have heart disease than females who did. The opposite is evidently true for males, more males had heart disease in the data set than males who did not have heart disease. 

@@

  \includegraphics[width=\textwidth]{Age_HeartDisease.png}

@@

  \includegraphics[width=\textwidth]{Cholesterol_Heart Disease.png}
  \caption{A comparative boxplot showing serum cholesterol level mg/dL for individuals in the data set with and without heart disease.}

@@

@@

  \includegraphics[width=\textwidth]{RBP_HeartDisease.png}

@@

\bibliography{refs}
\bibliographystyle{ama}
